\documentclass[letterpaper,10pt]{article}

% === Essential Packages ===
\usepackage[empty]{fullpage}             % Full page without headers/footers
\usepackage{titlesec}                    % Custom section titles
\usepackage{enumitem}                    % Adjustments for lists
\usepackage[hidelinks]{hyperref}         % URL linking without visible borders
\usepackage{fancyhdr}                    % Custom headers/footers
\usepackage{multicol}                    % Multiple column functionality
\usepackage{ragged2e}                    % Text alignment (ragged-right)

% === Fonts and Icons ===
\usepackage{fontawesome5}                % Font Awesome 5 icons
\usepackage{CormorantGaramond}           % Cormorant Garamond font
\usepackage{charter}                     % Charter font (used alongside CormorantGaramond)
\usepackage{xcolor}                      % Colors for customization

% === Document Metadata and Accessibility ===
\usepackage{bookmark}                    % PDF bookmarks
\usepackage{lastpage}                    % Reference to the last page for footers
\input{glyphtounicode}                   % Unicode support for ATS readability
\pdfgentounicode=1                       % Enable Unicode PDF

% === Color Customization ===
\definecolor{accentTitle}{HTML}{003c60}  % Title color
\definecolor{accentText}{HTML}{003c60}   % Text accent color
\definecolor{accentLine}{HTML}{6f7173}   % Line accent color

% === Page Setup ===
\pagestyle{fancy}                        % Enable fancy headers/footers
\fancyhf{}                               % Clear default header/footer
\fancyfoot{}                             % Remove footer by default
\renewcommand{\headrulewidth}{0pt}       % No header line
\renewcommand{\footrulewidth}{0pt}       % No footer line
\urlstyle{same}                          % Same font for URLs

% === Margins and Spacing Adjustments ===
\addtolength{\oddsidemargin}{-0.6in}     % Adjust margins
\addtolength{\topmargin}{-0.8in}         % Adjust top margin
\addtolength{\textwidth}{1.2in}          % Adjust text width
\addtolength{\textheight}{1.4in}         % Adjust text height

% === Spacing between elements ===
\setlength{\multicolsep}{-3.0pt}         % Multicolumn separation
\setlength{\tabcolsep}{0pt}              % Table column separation
\setlength{\columnsep}{-1pt}             % Column separation
\setlength{\footskip}{3.7pt}             % Footer spacing

% === Text Formatting ===
\raggedbottom                            % Avoid stretching text vertically
\raggedright                             % Left-align text

% === Custom Commands ===
\newcommand{\docTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle}#1}
    \vspace{3pt}
    {\color{accentLine} \hrule}
    \vspace{3pt}
    \footnotesize{#2}
    \vspace{3pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\iconHref}[4]{
  \href{#1}{\raisebox{#2\height}{#3}\ \ #4}
}

\titleformat{\section}{
  \vspace{-4pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[
  \vspace{2pt}
  \color{accentLine}\titlerule
  \vspace{-2pt}
]

\newcommand{\heading}[2]{
  \hspace{4pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{
    \textbf{\textit{\small{#2}}}
  }
}

\newcommand{\headingIt}[2]{
  \heading{{#1}}{
    \textit{\small{#2}}
  }
}

\newcommand{\educationFrag}[5]{
  \headingBf{#1}{#2}
  \hspace{-4pt}\headingIt{\textit{#3}}{#4}
  #5
}

\newcommand{\positionFrag}[3]{
  \vspace{3pt}
  \headingIt{\hspace{6pt}\underline{#1}}{#2}
  \vspace{2pt}
  \heading{\hspace{8pt}#3}{}
}

\newcommand{\experienceFrag}[4]{
    \headingBf{\href{#1}{#2{\normalfont{#3}}
  }}{}
  #4
}

\newenvironment{bulletList}{
  \begin{itemize}[itemsep=1pt, parsep=1pt, leftmargin=26pt]
}{
  \end{itemize}
}

\newcommand{\skillsFrag}[1]{
  \vspace{-10pt}\\
  \hspace{15pt}\textit{#1}
}

\newcommand{\capstoneFrag}[3]{
  \vspace{2pt}
  \hspace{5pt}\headingIt{Capstone:\ \underline{#1}}{{#2}}
  \vspace{-7pt}
  #3
}

\newcommand{\docFooter}[1]{
  \setlength{\footskip}{12pt}
  \fancyfoot[C]{\hspace{84pt} #1}
}

\newcommand{\numberedPages}{
  \docFooter{\thepage/\pageref{LastPage}}
}

\newcommand{\oneFrag}[4]{
  \headingBf{#1}{#2}
  \hspace{6pt}\textit{#3}
  \vspace{-4pt}
  #4
}

\newenvironment{nestedBulletList}{
  \begin{itemize}[itemsep=1pt, parsep=1pt, leftmargin=14pt]
}{
  \end{itemize}
}

\newcommand{\projectFrag}[6]{
  \headingBf{\href{#1}{#2}}{#3}
  \hspace{-4pt}\headingIt{\textit{#4}}{#5}
  \vspace{-6pt}
  \begin{bulletList}
    #6
  \end{bulletList}
}

\begin{document}

\numberedPages

% === Title ===

\docTitle{Eason Lim Yi Hong}{
  \iconHref{mailto:eason.yihong@gmail.com}{-0.1}{\faEnvelope}{eason.yihong@gmail.com} ~|~
  \iconHref{https://linkedin.com/in/eason-lim}{-0.04}{\faLinkedin}{linkedin.com/in/eason-lim} ~|~
  \iconHref{https://github.com/eesuhn}{-0.02}{\faGithub}{github.com/eesuhn} ~|~
  \iconHref{https://x.com/eesuhn}{-0.02}{\faTwitter}{x.com/eesuhn}
}

% === Summary ===

\vspace{-12pt}
\begin{justify}
  A versatile engineer with a diverse technical background, including Web3 and DevOps.
  Known for adaptability and a passion for continuous learning, I thrive in problem-solving and collaborative environments.
  Actively engaged in tech events and speaking engagements to drive innovation and share valuable insights.
\end{justify}

% === Education ===

\section{Education}

\educationFrag{
  Bachelor of Software Engineering (Hons)
}{
  Sept 23' -- Aug 25'
}{
  Lancaster University \textbar\ Sunway University
}{
  CGPA: 3.56
}{
  \capstoneFrag{AI-powered Note-Taking App}{Django · NLP · Machine Learning}{
    \begin{bulletList}
      \item Automatically generates fine-tuned notes from lecture videos and text-based inputs.
      \item Utilized NLP and reinforcement learning for content summarization and note improvement.
    \end{bulletList}
  }
}

\vspace{-2pt}
\educationFrag{
  Diploma in Information Technology
}{
  Aug 21' -- Aug 23'
}{
  Sunway College
}{
  CGPA: 3.98
}{
  \capstoneFrag{
    \href{https://github.com/eesuhn/tomodachi}{Gamified Habit Tracker}}{PHP · JavaScript · MySQL}{
    \begin{bulletList}
      \item Implemented game-like features to increase long-term retention and user engagement.
      \item Integrated a Tamagotchi-inspired virtual pet system to motivate users in building habits.
    \end{bulletList}
  }
}

% === Experience ===

\section{Experience}

\experienceFrag{https://www.coingecko.com/en/about}{
  CoinGecko
}{}{
  \positionFrag{Product Manager (Internship)}{Jan -- Present}{
    \vspace{-19pt}
    \begin{bulletList}
      \item Bridge the gap between business stakeholders and engineering teams.
      \item Focus on optimizing CoinGecko API and developer tools.
    \end{bulletList}
  }
}

\vspace{2pt}
\experienceFrag{https://www.42network.org}{
  42
}{-- Coding School}{
  \positionFrag{Cadet}{Feb 24' -- Present}{
    \vspace{-2pt}
    \skillsFrag{C · Shell Scripting · Linux}
    \vspace{-6pt}
    \begin{bulletList}
      \item Practical experience in low-level programming and system architecture through project-based learning.
      \item Collaborated in a peer-to-peer environment, building projects without standard libraries.
    \end{bulletList}
  }
  \vspace{-6pt}
  \positionFrag{Pisciner}{Jan 24'}{
    Completed a month-long coding boot camp focused on C programming.
  }
}

\vspace{10pt}
\experienceFrag{https://www.linkedin.com/company/fusionex-group}{
  Fusionex Group
}{-- Software House}{
  \positionFrag{Back-end Developer (Internship)}{Jun -- Aug 23'}{
    \vspace{-1pt}
    \skillsFrag{PHP · Laravel Lumen · Azure DevOps}
    \vspace{-6pt}
    \begin{bulletList}
      \item Developed RESTful APIs to enhance communication between web and mobile platforms.
      \item Delivered feature-specific modules to improve client reservation systems.
      \item Optimized SQL views, enhancing the overall product performance.
    \end{bulletList}
  }
}

\vspace{2pt}
\experienceFrag{https://consumer.huawei.com/my}{
  Huawei
}{}{
  \positionFrag{Sales Executive}{May 21' -- Present}{
    \vspace{-19pt}
    \begin{bulletList}
      \item Achieved 120\% of the annual sales target, generating MYR 300k in revenue for 2022.
      \item Strengthened brand partnerships, enhanced company reputation and market presence.
    \end{bulletList}
  }
}

\vspace{2pt}
\experienceFrag{https://www.linkedin.com/company/sunway-tech-club}{
  Sunway Tech Club (STC)
}{}{
  \positionFrag{Advisor}{Mar 24' -- Present}{
    Mentored the executive board and committees by providing strategic guidance and support.
  }
  \vspace{2pt}
  \positionFrag{Head of Marketing Department}{Apr 23 -- Mar 24'}{
    \vspace{-19pt}
    \begin{bulletList}
      \item Led a team of over 10 to strategize and execute marketing initiatives.
      \item Secured event collaborations, enhancing the club's visibility and engagement.
    \end{bulletList}
  }
  % \vspace{-6pt}
  % \positionFrag{Committee}{Jun 22' -- Mar 23'}{
  %   Contributed to marketing initiatives and helped boost event participation.
  % }
}

% \vspace{10pt}
% \experienceFrag{https://www.linkedin.com/company/sunway-student-ambassadors}{
%   Sunway Student Ambassadors
% }{-- Campus Organization}{
%   \positionFrag{Executive of Publicity \& Engagement}{Dec 22' -- Dec 23'}{
%     \vspace{-19pt}
%     \begin{bulletList}
%       \item Spearheaded the development of website, improving accessibility for students.
%       \item Managed social media platforms, boosting online engagement.
%     \end{bulletList}
%   }
% }

\newpage

% === Honors & Awards ===

\section{Honors \& Awards}

\vspace{2pt}
\oneFrag{
  \href{https://ethglobal.com/events/bangkok}{ETHGlobal Bangkok 2024}
}{
  Nov 24'
}{
  Global Ethereum Hackathon
}{
  \begin{bulletList}
    \item Built a DAO-like education platform enabling community governance through pool-staking.
    \item Awarded Pool Prize by \textbf{World} for \textbf{\href{https://ethglobal.com/showcase/decademy-8g59p}{Decademy}}, promoting learner-driven education.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  \href{https://ethglobal.com/events/singapore2024}{ETHGlobal Singapore 2024}
}{
  Sept 24'
}{
  Global Ethereum Hackathon
}{
  \begin{bulletList}
    \item Secured the following prizes:
    \vspace{-4pt}
    \begin{nestedBulletList}
      \item
      \textbf{Best Consumer Application} @ \textit{\href{https://sign.global}{Sign Protocol}}
      \item
      \textbf{Pool Prize} @ \textit{\href{https://worldcoin.org}{Worldcoin}}
    \end{nestedBulletList}
    \item Developed \textbf{\href{https://ethglobal.com/showcase/decentrust-vwp81}{DecenTRUST}} to utilize on-chain skill verification through merit-based assessments.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  \href{https://innovationlabs.sunway.edu.my}{Sunway's iLabs} --
  \href{https://x.com/SuperteamMY/status/1815758624716931379}{Make It Challenge 2024}
}{
  Jun 24'
}{
  Web3 x Net-Zero -- Solana Hackathon
}{
  \begin{bulletList}
    \item Awarded
    \textbf{First Runner-Up} and
    \textbf{Best Prototype}
    \item Built \textbf{\href{https://github.com/eesuhn/voltio}{Voltio}} for fractionalized clean energy investments via NFTs.
    \item Enabled users to earn sustainable returns via tokenized solar projects.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  \href{https://scholarship.sunway.edu.my/scholarship/jeffrey-cheah-foundation-scholarship}{Jeffrey Cheah Foundation Scholarship}
}{
  Aug 21', Sept 23'
}{
  Issued by
  \href{https://jeffreycheah.foundation}{Jeffrey Cheah Foundation (JCF)}
}{
  \begin{bulletList}
    \item Awarded full scholarships for:
    \vspace{-4pt}
    \begin{nestedBulletList}
      \item
      \textbf{Bachelor of Software Engineering (Hons)} @
      \textit{Lancaster University \textbar\ Sunway University}
      \item
      \textbf{Diploma in Information Technology} @
      \textit{Sunway College}
    \end{nestedBulletList}
    \item Recognized for academic excellence and leadership qualities in both instances.
  \end{bulletList}
}

% === Volunteer Work ===

\section{Volunteer Work}

\oneFrag{
  \href{https://www.2024.ethkl.org}{Ethereum Kuala Lumpur 2024 (ETHKL)}
}{
  Crew · Hackathon
}{
  Malaysia's Largest Ethereum Community
}{
  \begin{bulletList}
    \item Managed event logistics and supported participants during the hackathon.
    \item Assisted in organizing workshops and networking sessions.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  \href{https://www.linkedin.com/feed/update/urn:li:activity:7219932643142901760}{42 x Fugee School -- Pygame}
}{
  Tech Lead · Workshop
}{
  Game Development with 42
}{
  \begin{bulletList}
    \item Conducted a Python workshop for refugee students, teaching basic game development.
    \item Guided students in creating their own games using Pygame.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  \href{https://linktr.ee/project.eldercare}{Project ElderCare}
}{
  Lead · Veteran Support
}{
  Community Service
}{
  \begin{bulletList}
    \item Led a team of volunteers in organizing activities for elderlies.
    \item Raised funds through charity events to support the veterans' welfare.
  \end{bulletList}
}

% \vspace{2pt}
% \oneFrag{
%   \href{https://www.linkedin.com/feed/update/urn:li:activity:7092021655891316736}{Sunway's Got Talent 2023}
% }{
%   Committee · Event
% }{
%   Campus Annual Talent Show
% }{
%   \begin{bulletList}
%     \item Hosted 1,000+ attendees and managed event logistics.
%     \item Ensured smooth execution of the event, coordinating setup and scheduling.
%   \end{bulletList}
% }

\vspace{2pt}
\oneFrag{
  \href{https://www.linkedin.com/feed/update/urn:li:activity:7146880139035852800}{From Solo to Team Project}
}{
  Speaker · Workshop
}{
  DevOps with STC
}{
  \begin{bulletList}
    \item Presented DevOps basics and best practices to 130+ participants.
    \item Focused on Git version control and CI/CD pipelines.
  \end{bulletList}
}

\vspace{2pt}
\oneFrag{
  Google DevFest KL 2022
}{
  Emcee · Event
}{
  Malaysia's Google Developer Network
}{
  \begin{bulletList}
    \item Hosted 500+ attendees, introducing speakers and managing event flow.
    \item Facilitated networking sessions to enhance participant engagement.
  \end{bulletList}
}

\newpage

% === Projects ===

\section{Projects}

\projectFrag{
  https://github.com/eesuhn/decademy
}{
  Decademy
}{
  Ethereum · Education
}{
  Community-driven education platform
}{
  Next · Solidity · Hardhat · Bun
}{
  \item Empowers learners to shape education trends through
  \textbf{pool-staking} governance.
  \item Built on
  \textbf{Scroll Network} using ZK-rollups for scalability.
  \item Utilized
  \textbf{The Graph} for indexing on-chain data for real-time educational trends.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/decentrust
}{
  DecenTRUST
}{
  Ethereum · Recruitment
}{
  Bringing recruitment to the blockchain
}{
  Next · Solidity · Foundry
}{
  \item Focused on creating an anti-discriminatory recruitment process using merit-based assessments.
  \item Built on
  \textbf{Linea} network with
  \textbf{Dynamic} for seamless user authentication.
  \item Leveraging
  \textbf{Worldcoin} for human verification and
  \textbf{Sign Protocol} to attest assessment results.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/voltio
}{
  Voltio
}{
  Solana · NFT
}{
  Fractionalized clean energy investments
}{
  Anchor · Rust · React
}{
  \item Enables fractionalized investments in solar energy projects through
  \textbf{tokenized assets}.
  \item Offering returns in native tokens as ROI for investors.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/ruma
}{Ruma}{
  Solana · NFT
}{
  Event hosting with NFT
}{
  Next · Anchor · Rust
}{
  \item Host events directly on-chain.
  \item Enable attendees to mint NFTs as memories.
  \item Streamline authentication with NFT-based badges.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/Shukan
}{
  Shukan
}{
  Android · Mobile
}{
  Minimalist habit tracker
}{
  Kotlin · Jetpack Compose · Room
}{
  \item Achieved recognition with
  \textbf{more than 60 stars} on GitHub for its simplicity and usability.
  \item Enables users to track and maintain habit streaks, with progress visualized.
  \item Built using
  \textbf{Coroutines} for asynchronous tasks and follows
  \textbf{MVVM} architecture.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/piksel-bros
}{
  Piksel Bros.
}{
  Platformer · Game
}{
  Pixelated 2D adventure
}{
  Pygame · Python · Makefile
}{
  \item Created a 2D platformer with level editor and custom sprites.
  \item Developed a
  \textbf{custom physics engine} to facilitate dynamic character movement.
}

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/renew
}{
  Renew
}{
  Custom Framework
}{
  Marketplace for circular economy
}{
  PHP · JavaScript · MySQL
}{
  \item A sustainable marketplace for recycling items, and showcasing upcycled products.
  \item Built an
  \textbf{MVC framework} from scratch to improve reusability.
  \item Incorporated a router and view manager, enabling dynamic content rendering.
}

% \vspace{2pt}
% \projectFrag{
%   https://github.com/eesuhn/jiraffe
% }{
%   Jiraffe
% }{
%   Full-Stack · Web
% }{
%   Task management tool
% }{
%   MongoDB · Express · React · Node
% }{
%   \item Enables users to create, assign, and track tasks in a collaborative environment.
%   \item Implemented RESTful APIs with
%   \textbf{Express} for CRUD operations.
%   \item Utilized
%   \textbf{MongoDB} for dynamic data storage, enabling real-time updates.
% }

\vspace{2pt}
\projectFrag{
  https://github.com/eesuhn/42-libft
}{
  42-libft
}{
  Data Structures · Algorithms
}{
  Custom C library
}{
  C · Makefile
}{
  \item Developed a custom C library from scratch for 42's curriculum.
  \item Implemented Makefile for compilation and unit testing of functions.
}

% \vspace{2pt}
% \projectFrag{
%   https://github.com/eesuhn/Pokemon
% }{
%   Pokemon
% }{
%   OOP · Turn-based · Game
% }{
%   Classic Game-Boy title
% }{
%   Scala · SBT
% }{
%   \item Recreates original Pokemon battles, with turn-based combat and type effectiveness.
%   \item Developed an AI model that selects moves and switches based on game state.
%   \item Automated asset handling using Python
%   \textbf{(FFmpeg, BeautifulSoup)} to extract sprites and audio.
% }

\end{document}
